---
title: "Function2_Ex1_P3"
author: '48693'
date: "2024-10-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Transformation Function 1

This function takes an argument `data` and adds a new column, `total_crime`, which is a total of the murder, assault, and rape cases per 100,000 people in each U.S. state. This function works on the data set `USArrests`. 

```{r}
library(tidyverse)

total_crimes <- function(data) {
  mutated_data <- mutate(data, total_crime = Murder + Assault + Rape)
}
```

Here is the function being run on the data set `USArrests` and the resulting data frame. 

```{r}
updated_arrests <- total_crimes(USArrests)

print(updated_arrests)
```

## Transformation Function 2 

This function takes an argument `data` and, rather uselessly, makes it untidy. This function works on the data set `USArrests`. It takes the columns `Murder`, `Assault`, and `Rape` and makes them into one long column. A new column, `crime_type` is added to classify these crime rates into murder, assault, and rape cases. 

```{r}
untidier <- function(data){
  longer_data <- pivot_longer(data, cols = c(Murder, Assault, Rape), names_to = "crime_type", values_to = "count")
}

# To show what the function produces. 
untidy_data <- untidier(USArrests)
print(untidy_data)
```


